---
title: "colaborator"
format: html
editor: visual
---
# Set up
```{r}
#| warning: false
#| message: false
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

# Load data
```{r}
#| message: false
lobster_traps <- read_csv("../data/Lobster_Trap_Counts_All_Years_20210519.csv")
```

# Explore de data 
```{r}
str(lobster_traps)
colnames(lobster_traps)
```

# Conver -9999 to NA
```{r}
lobster_traps<- lobster_traps %>% mutate(TRAPS= na_if(TRAPS,-99999))
```
# Filter out NAPL site
```{r}
lobster_traps_filtered<- lobster_traps%>% filter(SITE != "NAPL")

```
# Create and store a subset with lobsters at Carpinteria Reef (CARP) OR number of commercial trap floats is greater than 20. Check your output.

```{r}
lobsters_trap_subset<- lobster_traps_filtered %>% filter(SITE=="CARP"|TRAPS>20)
```

## Create a multi-panel plot of lobster commercial traps (TRAPS) grouped by year, using ggplot(), geom_histogram(), and facet_wrap(). Use the variable YEAR in facet_wrap(). Use the object lobster_traps.
```{r}
#| warning: false
#| message: false
ggplot(lobster_traps,aes(x=TRAPS))+geom_histogram()+facet_wrap(~YEAR)
```

# clean site inconsistency
```{r}
lobster_traps<- lobster_traps %>% mutate(SITE= tolower(SITE)) %>% mutate(SITE=toupper(SITE))
```

### summary
```{r}
lobster_traps_summarize<- lobster_traps %>% group_by(SITE,YEAR) %>% 
  summarize(TOTAL_TRAPS= sum(TRAPS, na.rm=TRUE)) %>% 
  ggplot(aes(x=YEAR, y=TOTAL_TRAPS, colour=SITE))+geom_line()+
  labs(title= "Total traps by year",x="Year", y="Total traps", colour="Site")+
  theme_classic()
lobster_traps_summarize

```

### with points
```{r}
lobster_traps_withpoint<- lobster_traps %>% group_by(SITE,YEAR) %>% 
  summarize(TOTAL_TRAPS= sum(TRAPS, na.rm=TRUE)) %>% 
  ggplot(aes(x=YEAR, y=TOTAL_TRAPS, color=SITE))+geom_line()+geom_point()+
  labs(title= "Total traps by year",x="Year", y="Total traps", colour="Site")+
  scale_x_continuous(breaks=seq(2012,2022, 1))
  theme_classic()
lobster_traps_withpoint
ggsave("")
```

# new table with filters
```{r}
lobster_traps_fishing_pressure<- lobster_traps %>% filter(YEAR %in% c(2019, 2020,2021)) %>%  mutate(FISHING_PRESSURE= if_else(TRAPS>=8,"HIGH",'LOW')) %>% 
  group_by(FISHING_PRESSURE) %>% summarize(PRESSURE=n()) %>% drop_na()
ggplot(lobster_traps_fishing_pressure,aes(x=FISHING_PRESSURE,y=PRESSURE, fill = FISHING_PRESSURE))+geom_col(position = 'dodge')+labs(title="Fishing pressure",subtitle = "count", x="Fishing pressure")
```

